---
title: "future_problem_set"
author: "NAME HERE"
date: "10/13/2020"
output: pdf_document
---


## Part 2

### Question 7 / Challenge

Use the readxl library and load two data sets from the "two_data_sheets" file. There's a parameter that you can specify which sheet to load. In this case, we have data about rat reaction time in sheet 1 and home visits in sheet 2.

```{r, echo=T, results="markup"}
library(readxl)
df_rats <- read_excel("../data/two_data_sheets.xlsx", 1)
df_home <- read_excel("../data/two_data_sheets.xlsx", 2)
```

\newpage

### Question 8

For the rats data, pivot the data frame from wide to long format. We want the 1, 2, 3 columns, which represent the amount of cheese placed in a maze, to transform into a column called "cheese". The values in the cheese column will be the time, which represents the amount of time the rat took to complete the maze. Please use the head() function to print your data frame.

```{r}
# convert from wide to long
df_rats$subject <- factor(df_rats$subject)
df_rats_long <- df_rats %>% 
  pivot_longer(c(`1`, `2`, `3`), names_to = "cheese", values_to = "time")

head(df_rats_long)
```

\newpage 

### Question 9

Compute the mean and standard deviation of the maze time.

```{r}
df_rats_long %>%
  # organize by amount of cheese
  group_by(cheese) %>%
  # summarize
  summarize(mean = mean(time), # mean function
            sd = sd(time))     # standard deviation function
```

\newpage

### Question 10 

Last one (we promise). With the home visits data, pivot the data frame from long to wide. We want the names from the action column to become unique columns and the values to represent the counts. Please use the head() function to print your data frame.

```{r}
# pivot from long to wide
df_home_wide <- df_home %>%
  pivot_wider(names_from = action, values_from = count)

head(df_home_wide)
```
