---
title: "Introduction"
author: "Lawrence Y. Tello"
date: "8/15/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown Introduction

Welcome to PHW290: R for Public Health!

We're excited that you're here and look forward to a semester with you and R. The current file you are looking at is called a "RMarkdown", which has a .Rmd extension. We will use this type of R file for the semester due to its easy readability and capacity for creating *neat* PDF, HTML, and MS Word files. 
  
\newpage

### RMarkdown Basics

Below is a R chunk, which is where you type your code. You can run code line by line by holding down Ctrl/Command + Enter. If you want to run the entire chunk, you can click the green arrow on the right-hand side of the chunk. Try both of these methods for the code below!

```{r}
print("hello world")
```

```{r}
# this is a comment
# anything following a hash/number/pound sign within a R chunk is a comment. 
# comments are not evaluated
# for example, the following code will not run:

# print("hello world")
```

```{r}
# example of code running off the page
library(ggplot2)
ggplot(data = ChickWeight, aes(x = Time, y = weight, color = Diet, group = Chick)) + geom_line() + ggtitle("Growth curve for individual chicks")
```

Knitting shortcut: Alt + Shift + K