---
title: "Introduction"
author: "Lawrence Y. Tello"
date: "8/15/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown Introduction

Welcome to PHW290: R for Public Health!

We're excited that you're here and look forward to a semester with you and R. The current file you are looking at is called a "RMarkdown", which has a .Rmd extension. We will use this type of R file for the semester due to its easy readability and capacity for creating *neat* PDF, HTML, and MS Word files. 

Today we will cover:
  1. RMarkdown basics
  2. R as a calculator
  3. Variable assignment in R
  
## RMarkdown Basics

Below is a R chunk, which is where you type your code. You can run code line by line by holding down Ctrl/Command + Enter. If you want to run the entire chunk, you can click the green arrow on the right-hand side of the chunk. Try both of these methods for the code below!

```{r}
print("hello world")
```

```{r}
# this is a comment
# anything following a hash/number/pound sign within a R chunk is a comment. 
# comments are not evaluated
# for example, the following code will not run:

#print("hello world")
```

Fix the above chunk to print "hello world".

## R as a calculator

R is a powerful calculator. Let's see it in action. 

```{r}
1 + 1

1 / 0.00000001


```
Incredible.

Let's try

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
