---
title: "Problem Set 4"
author: "NAME HERE"
date: "9/17/2020"
output: pdf_document
---

Due date: Monday, September 28

For this problem set you will tidy up a dataset of 500 individuals. We also want to calculate each individual's BMI and appropriately categorize them.

Load your data:

```{r, include=FALSE}
library(tidyverse)
bmi <- read_csv("500_Person_Gender_Height_Weight.csv")
str(bmi)
```

### Question 1

Clean the column headers to have all lower case and no spaces and rename location_information to location.

```{r}
bmi_1 <- rename_with(bmi, ~ tolower(gsub(" ","_", .x, fixed=TRUE)))
bmi_1 <- rename(bmi_1, location = location_information)
```

\newpage 

### Question 2

Create a new variable that calculates BMI for each individual.

You will need to navigate the different system of measurements (metric vs imperial). Only the United States is using imperial.

* BMI calculation and conversions:
    + metric:   $BMI = weight (kg) / [height (m)]^2$
    + imperial: $BMI = 703 * weight (lbs) / [height (in)]^2$
    + 1 foot = 12 inches
    + 1 cm = 0.01 meter

Although there's many ways you can accomplish this task, we want you to use an if_else(). 

```{r}
bmi_2 <- bmi_1 %>%
  mutate(bmi = if_else(
    location %in% c("New York", "Colorado", "Hawaii"),
    (703 * weight)/(height * 12)^2, 
    (weight/(height/100)^2)))

head(bmi_2$bmi)
```

\newpage

### Question 3

Create a new variable that categorizes BMI with case_when():

* Underweight: Below 18.5
* Normal: 18.5-24.9
* Overweight: 25.0-29.9
* Obese: 30.0 and Above

```{r}
bmi_3 <- bmi_2 %>%
  mutate(bmi_cat = case_when(
    bmi >= 30.0    ~ "Obese",
    bmi >= 25    ~ "Overweight",
    bmi >= 18.5  ~ "Normal",
    TRUE            ~ "Underweight"))
```

Could we have used if_else()?  

Yup, we could have! It's a matter of preference and how you are approach the problem.

\newpage

### Question 4

Arrange your data by location and descending order of bmi.

```{r}
bmi_4 <- bmi_3 %>%
  arrange(location, desc(bmi))
```

### Question 5

Filter your data to remove the height, weight, and bmi column.

```{r}
bmi_5 <- bmi_4 %>% select(-c(height, weight, bmi))
```

\newpage

### Challenge

Perform all the actions in this problem set with one dpylr call. 

```{r}
bmi_all <- bmi %>% 
  rename_with(~ tolower(gsub(" ","_", .x, fixed=TRUE))) %>%
  rename(location = location_information) %>%
  mutate(bmi = if_else(location %in% c("New York", "Colorado", "Hawaii"),
                       (703 * weight)/(height * 12)^2, 
                       weight/(height/100)^2),
         bmi_cat = case_when(bmi > 30    ~ "Obese",
                             bmi > 25    ~ "Overweight",
                             bmi > 18.4  ~ "Normal",
                             TRUE        ~ "Underweight")) %>%
  arrange(location, desc(bmi)) %>%
  select(-c(height, weight, bmi)) 
  

head(bmi_all)
```
