---
title: "Problem Set 3"
author: "YOUR NAME HERE"
date: "DATE"
output: pdf_document
---

* Due date: Monday, September 21
* Submission process: Please submit your assignment directly to Gradescope. You can do this by knitting your file and downloading the PDF to your computer. Then navigate to Gradescope.com or via the link on BCourses to submit your assignment. 

Helpful hints:

- Knit your file early and often to minimize knitting errors! If you copy and paste code from the slides, you are bound to get an error that is hard to diagnose. Typing out the code is the way to smooth knitting. We recommend knitting your file each time after you write a few sentences/add a new code chunk, so you can detect the source of the knitting error more easily. This will save you and the teaching team time!

- Please make sure that your code does not run off the page of the knitted PDF. If it does, we can't see your work. To avoid this, have a look at your knitted PDF and ensure all the code fits in the file. When it doesn't, go back to your .Rmd file and add spaces (new lines) using hte return or enter key so that the code runs onto the next line.

--------------------------------------------------------------------------------
```{r}
library(tidyverse)
```

\newpage 

For this problem set we will use *fictional* data inspired by research on non-deceptive or open-label placebos. Non-deceptive placebos are placebos but without the deception. Some studies have found suggestions that, despite not being tricked, participants are reporting similar benefits to what they would have with placebos! You can read more here:

https://www.npr.org/sections/health-shots/2016/10/27/499475288/is-it-still-a-placebo-when-it-works-and-you-know-its-a-placebo

https://www.nature.com/articles/s41467-020-17654-y


### Question 1

Read in the data! To make it slightly more challenging we have changed the format from a .csv to .xlsx and "hidden" the data one level deeper in the /data folder. 

```{r}

```

### Question


You're done! Please knit to pdf and upload to gradescope. 