---
title: 'Problem Set #5'
author: "NAME HERE"
date: "9/23/2020"
output: pdf_document
---

Due date: Monday, October 5th

At this point in the course we have introduced a fair amount of code, which can be a lot to hold in our memory at once! Thankfully we we have search engines and these [helpful cheatsheets](https://rstudio.com/resources/cheatsheets/). You may find the Base R and Data Tranformation Cheatsheet helpful.

### Question 1

Below is a function that ought to return TRUE if x is an even number. However, we're having trouble receiving a value despite x == 4, which we know is an even number. Debug and explain why this error is occurring. 

```{r}
# note: %% is the "moduluo" operator, which returns the remainder of an operation
# try: 2 %% 2 (should equal 0 as 2/2 has no remainder)
# try: 5 %% 2 (should equal 1 as 5/2 has a remainder of 1)

return_even <- function(x){
  if (x %% 2 == 0) {
    return("I'm an even number!")
  }
}

x <- 4
return_even()
```

### Question 



```{r}

calculate_bmi <- function(height, weight){
  bmi = (703 * weight)/(height * 12)^2
  return(bmi)
}

calculate_bmi(5.94, 233.73)
```

    (703 * weight)/(height * 12)^2, 
    (weight/(height/100)^2)))


Below is a function that examines the date format and uses the appropriate date conversion function. However, among the three data sets we are working with today, there's an additional date format that is not included in this function. Add that functionality to the function.