---
title: "unused_problem_set_questions"
author: "David Connell"
date: "8/5/2021"
output: pdf_document
---

### Question 5

For this question use the reprex function discussed in lecture for each of the variable assignments.

Create four variables to represent the 2x2 table in Question 2. We suggest using a, b, c, and d to match the 2x2 format.

Using these variables, calculate the odds ratio again and assign it to a new variable.

```{r question_5}
# your code here
```






\newpage

###  Question 9

Missing data, ugh! Missing data are ubiquitous part of social, behavioral, and health sciences. R can help us find where missing data is present. For this question, please read the help documentation of this useful tool.

```{r is.na}
# pull up help documentation by putting a question mark before the function name
?is.na()
```

Use is.na() to find the missing data in the data frame created in Question 7. List this observation's available information and which column is NA.

```{r question_9}
# your code here
```

\newpage

### Challenge

Create a function that lets you add two numbers together. For example, if I had two arguments, 1 and 2, the output should result in 3. You can use the ?function help documentation and/or google. 

```{r challenge}
# your code here
```



